Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
age not relevant - all GCs are old

NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gyr \citep{forbesandbridges2010}. It resides in the outer halo 87.5 kpc \todo{[citation needed]} from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.

>>>>

NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
